Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-07-13 paper/sec-intro.tex
work in the paper

While the SM production rates for Higgs
pair production are small in all production modes,
and require the full integrated luminosity of the HL-LHC phase
to be accessed, double Higgs production rates can be substantially
enhanced in a variety of Beyond the SM (BSM) scenarios.
%
Feasibility studies of Higgs pair production in New Physics
models have been performed in a number of different frameworks,
including effective theories with higher-dimensional
operators and anomalous values of the
Higgs couplings~\cite{Nishiwaki:2013cma,Dall'Osso:2015aia,Azatov:2015oxa,Liu:2014rba,Goertz:2014qta,He:2015spf,Grober:2015cwa}, resonant production
in models such as extra dimensions~\cite{Gouzevitch:2013qca,Cooper:2013kia,No:2013wsa}, as well as
in the context of Supersymmetry or Two Higgs Doublet models (2HDMs)~\cite{Belyaev:1999kk,Han:2013sga,Hespel:2014sla,Wu:2015nba,Cao:2014kya,Ellwanger:2013ova}.

@@

In this work we revisit the feasibility of SM Higgs pair production by gluon-fusion
in the $4b$ final state.
%
 Our analysis is based on a combination of traditional cut-based
 methods with modern multivariate techniques
 (in particular feed-forward multi-layer neural networks),
 which lead to a substantial
  enhancement of the signal discrimination.
  %
  We account for  all relevant
  backgrounds, including the contribution from light jet fakes.
  %
  By combining the contribution from the boosted, intermediate and resolved
  topologies we achieve a signal significance of $S/\sqrt{B}\simeq 3.2$.
%
  Therefore, our strategy allow us to improve the
  potential of this final state even when considering a
  more realistic background modeling.

>>>>

While the SM production rates for Higgs
pair production are small in all production modes,
and require the full integrated luminosity of the HL-LHC phase
to be accessed, double Higgs production rates can be substantially
enhanced in a variety of Beyond the SM (BSM) scenarios.
%
Feasibility studies of Higgs pair production in New Physics
models have been performed in a number of different frameworks,
including Effective Field
Theories (EFTs) with higher-dimensional
operators and anomalous values of the
Higgs couplings~\cite{Nishiwaki:2013cma,Dall'Osso:2015aia,Azatov:2015oxa,Liu:2014rba,Goertz:2014qta,He:2015spf,Grober:2015cwa}, resonant production
in models such as extra dimensions~\cite{Gouzevitch:2013qca,Cooper:2013kia,No:2013wsa}, as well as
in the context of Supersymmetry or Two Higgs Doublet models (2HDMs)~\cite{Belyaev:1999kk,Han:2013sga,Hespel:2014sla,Wu:2015nba,Cao:2014kya,Ellwanger:2013ova}.

@@

In this work we revisit the feasibility of SM Higgs pair production by gluon-fusion
in the $4b$ final state.
%
 Our strategy is based on a combination of traditional cut-based
 methods with modern multivariate analysis (MVA)
 (in particular feed-forward multi-layer neural networks),
 which lead to a substantial
  enhancement of the signal discrimination.
  %
  We account for  all relevant
  backgrounds, including the contribution from light jet fakes.
  %
  By combining the contribution from the boosted, intermediate and resolved
  topologies we achieve a signal significance of $S/\sqrt{B}\simeq 3.2$.
%
  Therefore, our strategy allow us to improve the
  potential of this final state even when considering a
  more realistic background modeling.
